The low-frequency Murchison radio environment:\\interference analysis and mitigation

### 2014-10-02 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Updates

The \textsc{aoflagger} software provides a C++ library\footnote{\url{http://aoflagger.sourceforge.net/doc/api/}} that can be integrated in a pipeline, thereby minimizing reading/writing of data. We have written an MWA-specific preprocessing pipeline named \textsc{cotter} that uses the \textsc{aoflagger} library for RFI detection. Additionally, \textsc{cotter} performs the following steps: it converts the raw correlator files into \textsc{casa} measurement sets or uvfits files; applies bandpass gain corrections; corrects the phases for varying cable lengths; calculates the $uvw$-coordinates; applies phase tracking to the desired sky coordinates; flags samples from the correlator that are missing or incorrect; and allows averaging the observation in frequency or time direction to reduce the data volume. It also collects some statistics and writes these into a measurement set using the LOFAR quality statistics format\footnote{Described in ``MeasurementSet description for LOFAR version 2.08'' by Schoenmakers \& Renting.}. Various tools are available to analyse these statistics, e.g. the \textsc{aoqplot} tool that is part of the \textsc{aoflagger} software can plot the statistics over various dimensions in an interactive manner.

>>>>

The \textsc{aoflagger} software provides a C++ library\footnote{\url{http://aoflagger.sourceforge.net/doc/api/}} that can be integrated in a pipeline, thereby minimizing reading/writing of data. We have written an MWA-specific preprocessing pipeline named \textsc{cotter} that uses the \textsc{aoflagger} library for RFI detection. Additionally, \textsc{cotter} performs the following steps: it converts the raw correlator files into \textsc{casa} measurement sets or uvfits files; applies bandpass gain corrections; corrects the phases for varying cable lengths; calculates the $uvw$-coordinates; applies phase tracking to the desired sky coordinates; flags samples from the correlator that are missing or incorrect; and allows averaging the observation in frequency or time direction to reduce the data volume. It also collects various statistics and writes these into a measurement set using the LOFAR quality statistics format\footnote{Described in ``MeasurementSet description for LOFAR version 2.08'' by Schoenmakers \& Renting.}. Various tools are available to analyse these statistics, e.g. the \textsc{aoqplot} tool that is part of the \textsc{aoflagger} software can plot the statistics over various dimensions in an interactive manner.
